Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-17 paper/paper.tex
Renamed
Commented stuff out, made new bib file
Changed section headings. Started the bib file

%\documentclass[acmsmall,screen,review]{acmart}
\documentclass[acmconf,screen,review]{acmart}
\usepackage{todonotes}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Automated Metadata Generation for Biological Specimen Image Collections}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Joel Pepper}
\email{jcp353@drexel.edu}
%\orcid{1234-5678-9012}
\author{David Breen}
\author{Jane Greenberg}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}

@@

\section{Introduction}
Text~\ref{demo-intro}~\todo{Liney}
\section{Background}
Text~\todo[noline]{Do this}
\subsection{Related Work}
Text laskjf askldfj lkasdjfklasdj flkjsadklfjlsdka fjlksdjfkl sadjklfjlksda.
\section{Objectives}
Text
\section{Data Analysis}
Text
\section{Discussion}
Text \textit{texty text}~\cite{Lamport:LaTeX}
\section{Conclusion}
Text \textbf{text}

\pagebreak{}

\section{Introduction}~\label{demo-intro}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

@@

>>>>

%\documentclass[acmsmall,screen,review]{acmart}
\documentclass[acmconf,screen,review]{acmart}
\usepackage{todonotes}
\usepackage{comment}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Automated Metadata Generation for Fish Specimen Image Collections}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Joel Pepper}
\email{jcp353@drexel.edu}
%\orcid{1234-5678-9012}
\author{Jane Greenberg}
\author{David Breen}
\orcid{0002-1376-5008}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}

@@

\section{Introduction}
Text~\ref{demo-intro}~\todo{Liney}

\section{Related Work}
Text~\todo[noline]{Do this}
\subsection{History of Quality Metadata}
\subsection{Fish Image Analysis}

\cite{BockAlexander2018TITE}
\cite{KonovalovD2017RDfA}
\cite{Williams:2020:UIF}

\section{Methods}
Text
\section{Results}
Text
\section{Discussion}
Text \textit{texty text}%~\cite{Lamport:LaTeX}
\section{Conclusion}
Text \textbf{text}

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

\begin{comment}
\pagebreak{}
\section{Introduction}~\label{demo-intro}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

@@

\end{comment}
